---
title: "Gross Domestic Product"
author: "Selmane Fouad"
date: "September 14, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Synopsis

In this project, I uploaded the country gross domestic product for 2017 data set from the world bank website and I use R library called plotly to make world map shows each country with  GDP.


## Loading and processing the raw data

You can download the data from the world bank website <https://data.worldbank.org/data-catalog/GDP-ranking-table> .



```{r cars, message=FALSE, warning=FALSE}
library(plotly)
library(tidyr)
gdp<- read.csv("GDP.csv")
```

Here’s I include only the data I need for this project.


```{r}
gdp_country<- gdp[6:200,- c(2,3,6)]
colnames(gdp_country)<- c("Abr", "Country","GDP")

```

Let's change the GDP variable from factor to numeric.

```{r}

gdp_country$GDP <- as.character(gdp_country$GDP)
gdp_country$GDP<-gsub(",","",gdp_country$GDP)
gdp_country$GDP <- as.numeric(gdp_country$GDP)

```

Create hover text.

```{r}
gdp_country$hover <- paste(gdp_country$Country,'<br>',"GDP :",gdp_country$GDP)

```
 
After preparing the data now we can use plotly choropleth map to shows the country GDP.


````{r, message=FALSE, warning=FALSE}

plot_geo(data = gdp_country)%>% 
  add_trace(z= ~GDP,color= gdp_country$GDP,locations= ~Abr, text= gdp_country$hover)%>%
  layout(title ="Gross Domestic Product 2017")



```

